What We Eval in the Shadows

### 2021-04-17 paper/main.tex
Add note to 6.3

Similarly to JavaScript, there are also unnecessary uses of \eval. For example,
the \c{PerformanceAnalytics} package contains a function \c{chart.QQPlot} that
uses \eval to resolve a string into function and another to call it and assign
its results into a variable:
\begin{lstlisting}
  function (R, d="norm", dp, ...) {
	  q.f <- eval(parse(text=paste("q",d,sep=""))); z <- NULL
  	eval(parse(text=paste("z<-q.f(",dp,",...)")))
  }
\end{lstlisting}
  In both cases, there is no need for \eval and the function can be rewritten as
\begin{lstlisting}
  function (R, d="norm", dp, ...) {
	  q.f <- get(paste0("q",d)); z <- q.f(dp, ...)
  }
\end{lstlisting}
or even to a one-liner \c{do.call(paste0("q",d), as.list(dp, ...))}.

>>>>

Similarly to JavaScript, there are also unnecessary uses of \eval. For example,
the \c{PerformanceAnalytics} package contains a function \c{chart.QQPlot} that
uses \eval to resolve a string into function and another to call it and assign
its results into a variable:
\begin{lstlisting}
  function (R, d="norm", dp, ...) {
	  q.f <- eval(parse(text=paste("q",d,sep=""))); z <- NULL
  	eval(parse(text=paste("z<-q.f(",dp,",...)")))
  }
\end{lstlisting}
  In both cases, there is no need for \eval and the function can be rewritten as
\begin{lstlisting}
  function (R, d="norm", dp, ...) {
	  q.f <- get(paste0("q",d)); z <- q.f(dp, ...)
  }
\end{lstlisting}
or even to a one-liner \c{do.call(paste0("q",d), c(dp, list(...)))}.

The problem is that these cases are not easy to spot. Because of the
limits of dynamic analysis we only have a partial coverage and cannot determine
if for example \eval sites classified as \c{X, V} will not be eventually called
with an expression in a \c{F(), F(X)} or \c{F(F(X))} category.
